Linking watershed nutrient loading to estuary water quality with Generalized Additive Models

### 2023-08-08 Rebuttal_Letter/Rebuttal_Letter.Rmd

---
author: Michael Schramm
return-address: 
  - Texas A&M AgriLife
  - Texas Water Resources Institute
  - 1001 Holleman Drive E.
  - College Station, Texas 77840
return-short: Michael Schramm, 2118 TAMU, College Station, TX 77840
address:
  - Dr. James Latimer
  - Academic Editor
  - PeerJ Life & Environment

subject: Revised Manuscript
opening: Dear Dr. Latimer,
closing: Best regards,
signature: Michael Schramm

output: komaletter::komaletter
---

Thank you for the prompt and thorough review of my manuscript, "Linking watershed nutrient loading to estuary water quality with semiparametric models." I really appreciate the substantive and helpful comments from each of the reviewers. The final draft and
draft with differences marked are attached. Please note that the latexdiff tool
did not highlight the very minor changes in the abstract or references. I also would like to note the updated title based on comments from one reviewer.

Line by line comments and responses are included below (reviewer comments are italicized).
I have incorporated nearly all of the requested changes from the reviewers.

@@

*Lines 129-131: It would be helpful if you described how deep the water column is at the estuary sample locations and from what depth the samples that you analyzed were taken. A little more explanation of the estuary dynamics would be helpful too -- is this a stratified or well-mixed system, what is the range in salinity, is there a key season of concern for eutrophication?*

**Response:** I have added additional description of the estuary dynamics *(lines 101-108)*. Specifically mixing, turbidity, and salinity. Given the preliminary nature of this study, there is not a season of concern identified yet, so it is not included. *still need to add sample depth here*

*Lines 194-201: Some discussion is needed of how you dealt with temporal matching of flow and loads to concentrations in the estuary. I see in the discussion (line 373-374) that you matched flow and load estimated for the day of each sample. This approach should be explained in the methods, and I think you need some explanation is needed as to why that would be appropriate and/or how it may impact the results. As you discuss below, you might get better relationships (for Table 4, Lines 244-248) if you either lagged the match or matched an average load and flow from some reasonable period before the estuary sample date. If you had the ability to try some models like that, I think it may be a useful addition.*

**Response:** Dr. Marcus Beck made a similar comment in his review. This is now addressed
by incorporating cumulative flows and loads into the estuary models. **need to address this and justify it in the manuscript now**.

@@

*Lines 286-321: I think this discussion is too long comparing the TP yield first to the Dunn study, and then to 3 other studies. The TP yield estimate from your study is in the middle of the others, so you can condense this 2 paragraph discussion and simply say that you fall in the middle of other estimates and state briefly that there are reasons such as land use and flow variability that the estimates vary.*

**Response:** I agree, this section has been considerably condensed.

*Lines 360-361: It is probably worthwhile to note that the effect of flow you see in chlorophyll is very likely due to more nutrients coming in with high flows. I wouldn’t want a reader to think that since your flow-adjusted nutrient loads are not linked to chlorophyll that this means there is definitely no impact of nutrients on chlorophyll concentrations. Along those lines, I’d suggest in Line 350-251 you specific that “No relationships between flow-adjusted inorganic nitrogen or TP loadings with chlorophyll-a were observed”*

**Reviewer: Marcus Beck**
*This article describes the use of Generalized Additive Models (GAMs) to estimate nutrient loads entering Lavica Bay from the main inflows. The author uses these models to evaluate the anthropogenic contribution of nutrients to the bay through flow-normalization and to evaluate if these loads are related to long-term variation in estuarine water quality. Overall, this is a valuable paper that further validates the use of GAMs for long-term trend analysis and will have particular value for the management of this system. My comments below relate to either clarification or adjustment of the methods that authors should consider. If pursued, I consider these changes appropriate for a major revision.*

**Response:** I'm highly appreciative of these comments, they have substantially improved the manuscript.

@@

*My second concern about the models in eqns. 5-7 also relates to the flow and load variables. It’s stated on line 199-201 that flow-adjusted load values were used, which makes sense, but I don’t understand how this additional analysis differs from the flow-normalization in the previous section (lines 176 – 179). Why not just use the flow-adjusted loads from the previous models? Once this is clarified (or corrected), it might make more sense to change eqn 6 to include smoothers for ddate, yday, and flow-normalized load, and eqn 7 to included smoothers for ddate, yday, and load. These wouldn’t be “nested” models for AIC comparison, but would perhaps provide a better approach to evaluate loads related to natural or non-natural variation. I don’t see the value in including flow as a separate variable since it’s basically a surrogate for total load.*

**Response:** I am combining my response to both these comments since they are related. These are valid concerns and related to a comment made by Reviewer 3 (probably indicative that I better make a change here).

(1) I agree that it makes more sense to utilize the flow normalized loading estimates generated in the previous section. The methodology and results have been adjusted to correct this.

(2) I struggled with the concept of incorporating lag effects while developing these models, it didn't occur to me to utilize aggregated loads/flows. I believe this is an appropriate approach and will incorporate it into the models. However, since the estuary water quality data is not measured at equal intervals, the suggested aggregation method is potentially inappropriate. For example, if a quarterly measurement was missed you can end up aggregating 6 months of loads for a given data point instead of 3 months. Walker et al. (2021) found that after Hurricane Harvey (a massive magnitude storm) water quality impacts in Lavaca Bay and adjacent estuaries were restricted to a relatively short period, somewhere between 20 days and a few months. Based on this info, I am incorporating 1-day lagged, 20-day cumulative loads and flows into this set of models instead of the same day measures.

(3) In regard to the suggestion for changing equations 6 and 7 to utilize loads and flow-normalized loads instead of flow: I suspect there are a number of different approaches available here. While it is correct that the flow variable is essentially a surrogate for total load, inclusion does allow us to assess the relative contribution of "natural" or streamflow/load driven variation compared to the variation driven by flow-normalized loads or human activities. The lack of co-variation between flow normalized loads (in particular the aggregated loads) and the flow variable (shown below)

```{r out.width="75%"}
knitr::include_graphics("TP_plots.png")
```

@@

*Line 341: Replace “were” with “was”. *

*Line 395: Replace “suggest” with “such as”.*

*Line 420: Replace “provide” with “prove” or “be”.*

## References

Walker, Lily M., Paul A. Montagna, Xinping Hu, and Michael S. Wetz. 2021. “Timescales and Magnitude of Water Quality Change in Three Texas Estuaries Induced by Passage of Hurricane Harvey.” Estuaries and Coasts 44 (4): 960–71. https://doi.org/10.1007/s12237-020-00846-6.

### 2023-08-08 Schramm-2023-06-PeerJ/Schramm-2023-08-PeerJ.Rmd
incorporate new estuary models

---
title: Linking watershed nutrient loading to estuary water quality with semiparametric models
preprint: false
author: 
  - name: Michael Schramm
    affiliation: 1
    corresponding: true
    email: michael.schramm@ag.tamu.edu
affiliation:
  - code: 1
    address: Texas Water Resources Institute, Texas A\&M AgriLife Research, College Station, Texas, United States
abstract: >
  Evaluating estuary water quality responses to reductions (or increases) in nutrient loading attributed to on the ground management actions can be challenging due to the strong influence of environmental drivers on nutrient loads and non-linear relationships. This study applied semiparametric approaches to calculate watershed nutrient loads and assess responses in estuary water quality to seasonally-adjusted freshwater inflow and flow-adjusted nutrient loads in Lavaca Bay, Texas. Lavaca Bay is a secondary embayment on the Texas coast displaying early potential for eutrophication and water quality degradation. Use of flow-adjusted nutrient loads allowed the study to evaluate the response in water quality to changes in nutrient loads driven by anthropogenic sources. Cross-validation indicated that, despite data constraints, semiparametric models performed well at nutrient load prediction. Based on these models, delivered annual nutrient loads varied substantially from year to year. In contrast, minimal changes in flow-normalized loads indicate that nutrient loadings were driven by natural variation in precipitation and runoff as opposed to changes in management of nonpoint sources. Models indicated no evidence of long-term changes in dissolved oxygen or chlorophyll-*a* within Lavaca Bay. However, site specific long-term increases in both organic and inorganic nitrogen are concerning for their potential to fuel eutrophication. Further analysis found freshwater inflow had strong influences on nutrient and chlorophyll-*a* concentrations but there was no evidence that changes in watershed nutrient loading explained additional variation in dissolved oxygen or chlorophyll-*a* concentrations. In addition to providing a baseline assessment of watershed nutrient loading and water quality responses in the Lavaca Bay watershed, this study provides methodological support for the use of semiparametric models in load regression models and estuary assessments.
bibliography: bibliography.bib
output:
  rticles::peerj_article:
    citation_package: biblatex
biblio-style: apa
header-includes:
    - \usepackage{csquotes}
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}

@@

modelsummary::datasummary(`Station ID` * (`TP (mg/L)`+
                           `NO\\textsubscript{x} (mg/L)` +
                           `TKN (mg/L)` +
                           `Chlorophyll-\\textit{a} (ug/L)` +
                           `DO (mg/L)`) ~
                           Mean*Arguments(na.rm=TRUE) + SD*Arguments(na.rm=TRUE) + N,
                         data = df, output = "data.frame") |> 
  mutate(`Station ID` = c(rep("TCEQ-13383", 5), rep("TCEQ-13384", 5),
                          rep("TCEQ-13563", 5))) |> 
  rename("Parameter" = " ") |> 
  mutate(Method = rep(c("EPA 365.1", "EPA 353.2", "EPA 351.2", "EPA 445.0", "ASTM D888-09(C) and TCEQ SOP V1"),3),
         `AWRL\\textsuperscript{a}`= rep(c(0.06, 0.05, 0.2, 3, NA),3),
         `Criteria\\textsuperscript{b}` = rep(c(0.21,NA,NA,11.6,5),3)) |> 
  kbl(format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "Summary of estuary water quality samples collected between January 1, 2005 and December 31, 2020.") |> 
  column_spec(6, width = "3cm") |> 
  collapse_rows(columns = 1, latex_hline = "major") |> 
  footnote(alphabet = c("Ambient water reporting limit (AWRL) represents the highest concentration that can be used as a reporting limit by a laboratory for inclusion in the state's monitoring data.",
                        "The state of Texas has not adopted numeric criteria for nutrients, these criteria represent screening levels used by the state for assessment purposes. NO\\\\textsubscript{x} and TKN parameters are not currently screened by the state and do not have an associated screening level."),
           threeparttable = T,
           escape = F)

@@

where $\mu$ is the conditional expected response (nutrient concentration), $g()$ 
is the log link, and response variable was modeled as Gamma distributed with 
mean $\mu$ and scale $\lambda$. $f_1(ddate)$ is decimal date smoothed with a 
thin-plate regression spline, $f_2(yday)$ is the numeric day of year smoothed 
with a cyclic cubic regression spline, $f_3(Q)$ is mean daily inflow (the 
combined measurements from Lavaca River and Navidad River) and $f_4(Load)$ is 
the total NO~3~ or TP watershed load. The set of models specified for each water
quality response are in Table\ \ref{tab:table3}.

@@

Because streamflow and nutrient loads are tightly correlated, freshwater inflow
can mask signals due to changes in nutrient loads alone. Following the 
methodology implemented by @murphyNutrientImprovementsChesapeake2022,
both freshwater inflow and nutrient loads were prepossessed to account for season
and streamflow respectively. Raw freshwater inflow values were replaced by 
seasonally adjusted log transformed inflow obtained from the residuals of a GAM model 
fit between season(day of year) and log transformed daily freshwater inflow. Raw nutrient
loads were replaced with flow-adjusted values obtained from the residuals of a
GAM model relating log transformed NO~3~ or TP loads to log transformed daily
inflow. Response residuals from the respective GAM models were 
used as *Q* and *Load* in Eq.\ \ref{eq6} and Eq.\ \ref{eq7}.

@@

dplyr::bind_rows(
    tar_read(tp_13563, store = store),
    tar_read(tp_13383, store = store),
    tar_read(tp_13384, store = store),
    tar_read(no3_13563, store = store),
    tar_read(no3_13383, store = store),
    tar_read(no3_13384, store = store),
    tar_read(chla_13563, store = store),
    tar_read(chla_13383, store = store),
    tar_read(chla_13384, store = store),
    tar_read(do_13563, store = store),
    tar_read(do_13383, store = store),
    tar_read(do_13384, store = store),
    tar_read(tkn_13563, store = store),
    tar_read(tkn_13383, store = store),
    tar_read(tkn_13384, store = store)
    ) |>
  mutate(Parameter = case_when(
    Parameter == "Nitrite+Nitrate" ~ "NO\\textsubscript{x}",
    Parameter == "Chlorophyll-a" ~ "Chlorophyll-\\textit{a}",
    TRUE ~ as.character(Parameter)),
    Model = case_when(
      Model == "Temporal" ~ "Temporal",
      Model == "Flow" ~ "Inflow",
      Model == "Flow + Load" ~ "Inflow + Load",
      TRUE ~ as.character(Model)
    )) |>
  mutate(Parameter = fct_relevel(Parameter, "TP", "NO\\textsubscript{x}", "Chlorophyll-\\textit{a}","TKN", "DO"),
         Model = fct_relevel(Model, "Temporal", "Inflow", "Inflow + Load")) |>
  tidyr::complete(Site, Model, nesting(Parameter)) |>
  mutate(model_prob = paste0(round(AICc,1), " (", round(weight,2), ")")) |>
  mutate(model_prob = case_when(
    model_prob == "NA (NA)" ~ "-",
    model_prob != "NA (NA)" ~ model_prob
  )) |>
  select(-c(AICc, weight)) |>
  pivot_wider(names_from = Model, values_from = model_prob) |>
  select(Parameter, Site, Temporal, Inflow, `Inflow + Load`) |>
  arrange(Parameter, Site) |>
  kbl(format = "latex",
      caption = "Estuary GAM AIC\\textsubscript{c} values and associated model probabilities (in parenthesis). Models with the highest probability for each site and water quality parameter combination are bolded and italicized for emphasis.",
      booktabs = TRUE, escape = FALSE) |> 
  column_spec(column = 3, 
              bold = c(F,F,F,F,F,F,F,T,F,T,T,F,T,T,F),
              italic = c(F,F,F,F,F,F,F,T,F,T,T,F,T,T,F)) |> 
  column_spec(column = 4, 
              bold = c(F,T,F,T,F,T,T,F,T,F,F,T,F,F,T),
              italic = c(F,T,F,T,F,T,T,F,T,F,F,T,F,F,T)) |> 
  column_spec(column = 5,
              bold = c(T,F,T,F,T,F,F,F,F,F,F,F,F,F,F),
              italic = c(T,F,T,F,T,F,F,F,F,F,F,F,F,F,F)) |> 
  collapse_rows(columns = 1, latex_hline = "major")

@@

comp <- compare_smooths(model = `TCEQ-13383`,
                      `TCEQ-13384` = tar_read(tp_lavaca_13384_full, store = store),
                      `TCEQ-13563` = tar_read(tp_lavaca_13563_full, store = store),
                      smooths = c("s(TP_resid)"),
                      overall_uncertainty = FALSE)
p_tp <- draw_smoothed_surface(comp,
                      x = TP_resid,
                      xlab = "Residuals log(TP) Load [kg]",
                      ylab = "TP [mg/L]",
                      subtitle = "A")

@@

comp <- compare_smooths(model = `TCEQ-13383`,
                      `TCEQ-13384` = tar_read(no3_lavaca_13384_full, store = store),
                      `TCEQ-13563` = tar_read(no3_lavaca_13563_full, store = store),
                      smooths = c("s(NO3_resid)"),
                      overall_uncertainty = FALSE)
p_no3 <- draw_smoothed_surface(comp,
                      x = NO3_resid,
                      xlab = "Residuals log(NO<sub>3</sub>) Load [kg]",
                      ylab = "NO<sub>*x*</sub> [mg/L]",
                      subtitle = "B")

>>>>

---
title: Linking watershed nutrient loading to estuary water quality with Generalized Additive Models
preprint: false
author: 
  - name: Michael Schramm
    affiliation: 1
    corresponding: true
    email: michael.schramm@ag.tamu.edu
affiliation:
  - code: 1
    address: Texas Water Resources Institute, Texas A\&M AgriLife Research, College Station, Texas, United States
abstract: >
  Evaluating estuary water quality responses to reductions (or increases) in nutrient loading attributed to on the ground management actions can be challenging due to the strong influence of environmental drivers on nutrient loads and non-linear relationships. This study applied semiparametric approaches to calculate watershed nutrient loads and assess responses in estuary water quality to seasonally-adjusted freshwater inflow and flow-adjusted nutrient loads in Lavaca Bay, Texas. Lavaca Bay is a secondary embayment on the Texas coast displaying early potential for eutrophication and water quality degradation. Use of flow-adjusted nutrient loads allowed the study to evaluate the response in water quality to changes in nutrient loads driven by anthropogenic sources. Cross-validation indicated that, despite data constraints, semiparametric models performed well at nutrient load prediction. Based on these models, delivered annual nutrient loads varied substantially from year to year. In contrast, minimal changes in flow-normalized loads indicate that nutrient loadings were driven by natural variation in precipitation and runoff as opposed to changes in management of nonpoint sources. Models indicated no evidence of long-term changes in dissolved oxygen or chlorophyll-*a* within Lavaca Bay. However, site specific long-term increases in both organic and inorganic nitrogen are concerning for their potential to fuel eutrophication. Further analysis found freshwater inflow had strong influences on nutrient and chlorophyll-*a* concentrations but there was no evidence that changes in watershed nutrient loading explained additional variation in dissolved oxygen or chlorophyll-*a* concentrations. In addition to providing a baseline assessment of watershed nutrient loading and water quality responses in the Lavaca Bay watershed, this study provides methodological support for the use of semiparametric models in load regression models and estuary assessments.
bibliography: bibliography.bib
output:
  rticles::peerj_article:
    citation_package: biblatex
biblio-style: apa
header-includes:
    - \usepackage{csquotes}
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}

@@

modelsummary::datasummary(`Station ID` * (`TP (mg/L)`+
                           `NO\\textsubscript{x} (mg/L)` +
                           `TKN (mg/L)` +
                           `Chlorophyll-\\textit{a} (ug/L)` +
                           `DO (mg/L)`) ~
                           Mean*Arguments(na.rm=TRUE) + SD*Arguments(na.rm=TRUE) + N,
                         data = df, output = "data.frame") |> 
  mutate(`Station ID` = c(rep("TCEQ-13383", 5), rep("TCEQ-13384", 5),
                          rep("TCEQ-13563", 5))) |> 
  rename("Parameter" = " ") |> 
  mutate(`Station ID` = case_when(
    `Station ID` == "TCEQ-13383" ~ "TCEQ-13383, Upper-Bay",
    `Station ID` == "TCEQ-13384" ~ "TCEQ-13384, Lower-Bay",
    `Station ID` == "TCEQ-13563" ~ "TCEQ-13563, Mid-Bay"),
         Method = rep(c("EPA 365.1", "EPA 353.2", "EPA 351.2", "EPA 445.0", "ASTM D888-09(C) and TCEQ SOP V1"),3),
         `AWRL\\textsuperscript{a}`= rep(c(0.06, 0.05, 0.2, 3, NA),3),
         `Criteria\\textsuperscript{b}` = rep(c(0.21,NA,NA,11.6,5),3)) |>
  mutate(`Station ID` = fct_relevel(`Station ID`,
                                    "TCEQ-13383, Upper-Bay",
                                    "TCEQ-13563, Mid-Bay",
                                    "TCEQ-13384, Lower-Bay")) |> 
  kbl(format = "latex", booktabs = TRUE, escape = FALSE,
      caption = "Summary of estuary water quality samples collected between January 1, 2005 and December 31, 2020.") |> 
  column_spec(1, width = "2cm") |>
  column_spec(6, width = "2.5cm") |> 
  collapse_rows(columns = 1, latex_hline = "major") |> 
  footnote(alphabet = c("Ambient water reporting limit (AWRL) represents the highest concentration that can be used as a reporting limit by a laboratory for inclusion in the state's monitoring data.",
                        "The state of Texas has not adopted numeric criteria for nutrients, these criteria represent screening levels used by the state for assessment purposes. NO\\\\textsubscript{x} and TKN parameters are not currently screened by the state and do not have an associated screening level."),
           threeparttable = T,
           escape = F)

@@

where $\mu$ is the conditional expected response (nutrient concentration), $g()$ 
is the log link, and response variable was modeled as Gamma distributed with 
mean $\mu$ and scale $\lambda$. $f_1(ddate)$ is decimal date smoothed with a 
thin-plate regression spline, $f_2(yday)$ is the numeric day of year smoothed 
with a cyclic cubic regression spline.
Prior work has shown that many water quality parameters may have lagged effects 
lasting days or even months following storms and large discharge events [@mooneyWatershedExportEvents2012a; 
@wetzExtremeFutureEstuaries2013; @bukaveckasInfluenceStormEvents2020; 
@walkerTimescalesMagnitudeWater2021]. @walkerTimescalesMagnitudeWater2021 showed
the impact of large flow events like Hurricane Harvey had somewhat short
water quality impacts in Lavaca Bay and adjacent estuary systems, ranging 
somewhere around 20 days to a few months. We incorporate this lag effect by using
cumulative totals for $f_3(Q)$ and $f_4(Load)$. $f_3(Q)$ is the cumulative of the 
previous 20 days of inflow (combined measurements from Lavaca River and 
Navidad River) and $f_4(Load)$ is the cumulative of the previous 20 days 
total NO~3~ or TP watershed load, both smoothed with thin plate regression 
splines. The set of models specified for each water
quality response are in Table\ \ref{tab:table3}.

@@

Because streamflow and nutrient loads are tightly correlated, freshwater inflow
can mask signals due to changes in nutrient loads alone. Following the 
methodology implemented by @murphyNutrientImprovementsChesapeake2022,
both freshwater inflow and nutrient loads were prepossessed to account for season
and streamflow respectively. Cumulative inflow values were replaced by 
seasonally adjusted cumulative inflow obtained from the residuals of a GAM model 
fit between season(day of year) and log transformed cumulative inflow. Nutrient
loads utilized the flow-normalized loads estimated in the previous section.

@@

dplyr::bind_rows(
    tar_read(tp_13563, store = store),
    tar_read(tp_13383, store = store),
    tar_read(tp_13384, store = store),
    tar_read(no3_13563, store = store),
    tar_read(no3_13383, store = store),
    tar_read(no3_13384, store = store),
    tar_read(chla_13563, store = store),
    tar_read(chla_13383, store = store),
    tar_read(chla_13384, store = store),
    tar_read(do_13563, store = store),
    tar_read(do_13383, store = store),
    tar_read(do_13384, store = store),
    tar_read(tkn_13563, store = store),
    tar_read(tkn_13383, store = store),
    tar_read(tkn_13384, store = store)
    ) |>
  mutate(Parameter = case_when(
    Parameter == "Nitrite+Nitrate" ~ "NO\\textsubscript{x}",
    Parameter == "Chlorophyll-a" ~ "Chlorophyll-\\textit{a}",
    TRUE ~ as.character(Parameter)),
    Model = case_when(
      Model == "Temporal" ~ "Temporal",
      Model == "Flow" ~ "Inflow",
      Model == "Flow + Load" ~ "Inflow + Load",
      TRUE ~ as.character(Model)),
    Site = case_when(
      Site == "TCEQ-13563" ~ "Mid-Bay",
      Site == "TCEQ-13383" ~ "Upper-Bay",
      Site == "TCEQ-13384" ~ "Lower-Bay"
    )) |>
  mutate(Parameter = fct_relevel(Parameter, "TP", "NO\\textsubscript{x}", "Chlorophyll-\\textit{a}","TKN", "DO"),
         Model = fct_relevel(Model, "Temporal", "Inflow", "Inflow + Load"),
         Site = fct_relevel(Site, "Upper-Bay", "Mid-Bay", "Lower-Bay")) |>
  tidyr::complete(Site, Model, nesting(Parameter)) |>
  mutate(model_prob = paste0(round(AICc,1), " (", round(weight,2), ")")) |>
  mutate(model_prob = case_when(
    model_prob == "NA (NA)" ~ "-",
    model_prob != "NA (NA)" ~ model_prob
  )) |>
  select(-c(AICc, weight)) |>
  pivot_wider(names_from = Model, values_from = model_prob) |>
  select(Parameter, Site, Temporal, Inflow, `Inflow + Load`) |>
  arrange(Parameter, Site) |>
  kbl(format = "latex",
      caption = "Estuary GAM AIC\\textsubscript{c} values and associated model probabilities (in parenthesis). Models with the highest probability for each site and water quality parameter combination are bolded and italicized for emphasis.",
      booktabs = TRUE, escape = FALSE) |>
  column_spec(column = 3,
              bold = c(F,F,F,F,F,F,F,F,T,T,F,T,T,F,T),
              italic = c(F,F,F,F,F,F,F,F,T,T,F,T,T,F,T)) |>
  column_spec(column = 4,
              bold = c(F,F,T,T,T,F,T,T,F,F,T,F,F,T,F),
              italic = c(F,F,T,T,T,F,T,T,F,F,T,F,F,T,F)) |>
  column_spec(column = 5,
              bold = c(T,T,F,F,F,T,F,F,F,F,F,F,F,F,F),
              italic = c(T,T,F,F,F,T,F,F,F,F,F,F,F,F,F)) |>
  collapse_rows(columns = 1, latex_hline = "major")

@@

comp <- compare_smooths(model = `TCEQ-13383`,
                      `TCEQ-13384` = tar_read(tp_lavaca_13384_full, store = store),
                      `TCEQ-13563` = tar_read(tp_lavaca_13563_full, store = store),
                      smooths = c("s(sum_TP_FN)"),
                      overall_uncertainty = FALSE)
p_tp <- draw_smoothed_surface(comp,
                      x = sum_TP_FN,
                      xlab = "Residuals log(TP) Load [kg]",
                      ylab = "TP [mg/L]",
                      subtitle = "A")

@@

comp <- compare_smooths(model = `TCEQ-13383`,
                      `TCEQ-13384` = tar_read(no3_lavaca_13384_full, store = store),
                      `TCEQ-13563` = tar_read(no3_lavaca_13563_full, store = store),
                      smooths = c("s(sum_NO3_FN)"),
                      overall_uncertainty = FALSE)
p_no3 <- draw_smoothed_surface(comp,
                      x = sum_NO3_FN,
                      xlab = "Residuals log(NO<sub>3</sub>) Load [kg]",
                      ylab = "NO<sub>*x*</sub> [mg/L]",
                      subtitle = "B")
